### 2015-06-25 reports/paper/introduction.tex
thesis update
udpate

In this paper, we first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.

>>>>

\section{Contribution}
In this thesis, we provided a detailed simulation of the impact of the arriving time estimation's accuracy on the localization error. We evaluated different array architectures, and showed that a two array architecture achieves better localization accuracy compared to a single array of similar physical size. We implemented and built the proposed sound localization system and compared differetn state of the art methods for localization and tracking. We also 
In this thesis, we first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.
